### 2017-05-24 scheduling/article/article.tex
Working on plots

@@

@@

@@

@@

@@

>>>>

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_10_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_10_1}
			\end{figure}

@@

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_20_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_20_1}
			\end{figure}

@@

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_30_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_30_1}
			\end{figure}

@@

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_40_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_40_1}
			\end{figure}

@@

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_100_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_100_1}
			\end{figure}

@@

			\begin{figure}[h]
				\begin{center}
					\begin{tikzpicture}
						\begin{axis}[
							symbolic x coords={Disyuntivo (100 secs.), Indices de Tiempo (100 secs.),Seleccion aleatoria (100 iters),Seleccion aleatoria (1000 iters), Busqueda Local (1 iters), Busqueda Local (4 iters)},
							width=\textwidth,
							height=0.5\textwidth,
							xtick=data,
							ybar,
							ymajorgrids,
							bar width=1.85cm,
							x tick label style={text width=2.15cm}]
							\addplot table [x=model, y=delay, col sep=comma] {../results/csv/sched_200_1.csv};
						\end{axis}
					\end{tikzpicture}
				\end{center}
				\caption{[TODO ]}
				\label{plot:sol-sched_200_1}
			\end{figure}
